Irt plot extra

### 2022-03-24 manuscript.Rmd
Table 1 label is hardcoded

A quantitative cross-sectional fully anonymous online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (https://enlightenyourclock.org/participate-in-research) of the science-communication comic-book "Enlighten your clock" co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux]. The landing page of the online survey had the explanatory statements where we mentioned participation was voluntary and that respondents could withdraw from participation anytime without being penalized. At the beginning of the survey, for the adult participants (>18 years) consent was recorded digitally. Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians. The entire survey was estimated to take <30 minutes. Participants were not compensated. As a part of the demographic information participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language. The demographic characteristics of our sample are given in Table \@ref(tab:demotab).To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention. What is 4+5?"). Participants were asked to confirm that they were participating the survey for the first time. Questions incorporating retrospective recall were all aligned to the period of "past four weeks".  
We conducted two rounds of data collections. At first we collected data for from `r nrow(EFA.descriptives)` participants  In the second round we collected data from another `r nrow(CFA.descriptives)` participants making a total sample of `r nrow(desctable.data)`.

>>>>

A quantitative cross-sectional fully anonymous online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (https://enlightenyourclock.org/participate-in-research) of the science-communication comic-book "Enlighten your clock" co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux]. The landing page of the online survey had the explanatory statements where we mentioned participation was voluntary and that respondents could withdraw from participation anytime without being penalized. At the beginning of the survey, for the adult participants (>18 years) consent was recorded digitally. Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians. The entire survey was estimated to take <30 minutes. Participants were not compensated. As a part of the demographic information participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language. The demographic characteristics of our sample are given in Table 1.To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention. What is 4+5?"). Participants were asked to confirm that they were participating the survey for the first time. Questions incorporating retrospective recall were all aligned to the period of "past four weeks".  
We conducted two rounds of data collections. At first we collected data for from `r nrow(EFA.descriptives)` participants.  In the second round we collected data from another `r nrow(CFA.descriptives)` participants making a total sample of `r nrow(desctable.data)`.
